\tool: Revisiting BadUSB with Type-C

### 2021-01-30 WOOT/Files/experiment.tex
done with case study backgound .

\subsection{Case study}
\label{subsec:case_study}
\subsubsection{Background}

@@

\textbf{Sharing Power Bank}.  Sharing power bank provides users with short-term
rental of power banks.  The company deploys power bank stations in the city and
users can rent a power bank from any of the power bank station, charge their
device on the trip, return the rented power bank to the near station, and pay
the rental fee.

For example, Brick~\cite{Brick} is such a power bank sharing service
provider from Sweden. It provides power bank rental service all over Sweden
and is planning on expanding its service around Europe. Moreover, this
service is even more popular in Asia, power bank stations are deployed in
markets, stores, and even newsstands.
%This suggests that this service is becoming more and more common around the global, especially in Asia and Europe.
\shuqing{I think we should paraphrase instead of using the descriptions on the website directly. Just to explain \textbf{what we need}.}

\fengwei{Explain the figure in the text.}
\begin{figure}[t]
	\centering
	\includegraphics[width=.45 \linewidth, height=.45 \linewidth]{./Figs/PBS_mt.png}
	\includegraphics[width=.45 \linewidth, height=.45 \linewidth]{./Figs/PBS_xd.png}
	\caption{Two Power Bank Stations}
	\label{fig:PBS_products}
\end{figure}

\yechang{add hyperlink or reference to Brick's website or Brick App on App Store/Google Play.}

@@

\textbf{QR Code Payment}.
QR code payment is a new type of payment method that is popular in Asia. Its most well-known cases are WeChat Pay~\cite{Wechat-pay} and Alipay~\cite{AliPay}. QR code payment provides merchant and client a convenient way of offline payment while ensuring equivalent security as the credit card.
As illustrated in Figure~\ref{fig:qr_payment_procedure}, QR code payment is typically performed in the following steps:
\ding{182} The client presents the payment QR code on the mobile device to the merchant.
The QR code is encoded with a globally unique ID to identify the client's account.
\ding{183} The merchant scans the payment QR code and charges the corresponding amount of money.
By presenting this QR code, the client authorizes the proceeding transaction.
\ding{184} After confirmation, the payment service provider proceed with this transaction and return the payment result to both the merchant and the client.
\shuqing{I think this paragraph can be shorter. No need to explain so many details.}
\hongyi{Dont know how to be more concise.}

@@

In the real-world scenario, some payment service providers use special rules
for micropayment purchases.  A micropayment is pre-determined by the payment
service provider with thresholds in the user agreement.  For example, WeChat
Pay~\cite{Wechat-pay} regards transaction under USD \textdollar 154 as
micropayments.  Different from a typical payment procedure, when micropayments
are made, confirmations can be applied automatically without clients'
permission which aims to provide convenience to both merchant and client.  If a
victim's payment code is leaked to the attackers, they can use that code to
authorize multiple micropayments without permission.  In order to prevent such
cases, both WeChat Pay~\cite{Wechat-pay} and Alipay~\cite{AliPay} has designed a refreshing mechanism for the
payment code, which is to refresh the QR code every minute. This is sufficient
to stop an attack like sneak shots but unable to stop a real-time attack like our
\tool.  In summary, the payment QR code is highly sensitive on users' devices
and our following case study is about how to obtain this code using an
attacker-crafted power bank via \tool.

>>>>

\subsection{Case study}
\label{subsec:case_study}

\subsubsection{Background}

@@

\textbf{Sharing Power Bank}.  Sharing power bank provides users with short-term
rental of power banks.  The company deploys power bank stations in the city and
users can rent a power bank from any of the power bank stations, charge their
device on the trip, return the rented power bank to the near stations, and pay
the rental fee.

For example, Brick~\cite{Brick} is such a power bank sharing service
provider from Sweden. It provides power bank rental service all over Sweden
and part of the Europe. Moreover, this
service is even more popular in Asia, power bank stations are deployed in
markets, stores, and even newsstands.
%This suggests that this service is becoming more and more common around the global, especially in Asia and Europe.
%\shuqing{I think we should paraphrase instead of using the descriptions on the website directly. Just to explain \textbf{what we need}.}

%\fengwei{Explain the figure in the text.}

\begin{figure}[t]
	\centering
	\includegraphics[width=.45 \linewidth, height=.45 \linewidth]{./Figs/PBS_mt.png}
	\includegraphics[width=.45 \linewidth, height=.45 \linewidth]{./Figs/PBS_xd.png}
	\caption{Two Power Bank Stations.}
	\label{fig:PBS_products}
\end{figure}

%\yechang{add hyperlink or reference to Brick's website or Brick App on App Store/Google Play.}

@@

\textbf{QR Code Payment}.
QR code payment is a new type of payment method that is popular in Asia. Its most well-known cases are WeChat Pay~\cite{Wechat-pay} and Alipay~\cite{AliPay}. QR code payment provides merchant and client a convenient way of offline payment while ensuring equivalent security as the credit card.
As illustrated in Figure~\ref{fig:qr_payment_procedure}, QR code payment is typically performed in the following steps:
\ding{182} The client presents the payment QR code on the mobile device to the merchant.
The QR code is encoded with a globally unique ID to identify the client's account.
\ding{183} The merchant scans the payment QR code and charges the corresponding amount of money.
By presenting this QR code, the client authorizes the proceeding transaction.
\ding{184} After confirmation, the payment service provider proceeds with this transaction and returns the payment result to both the merchant and the client.
\shuqing{I think this paragraph can be shorter. No need to explain so many details.}
\hongyi{Dont know how to be more concise.}

@@

Next, we explain one type of payments called micropayment. A micropayment is pre-determined by the payment
service provider with thresholds in the user agreement. In real-world scenarios, payment service providers use different rules
for micropayment purchases. For example, WeChat
Pay~\cite{Wechat-pay} regards transaction under USD \textdollar 154 as
micropayments.  Different from a typical payment procedure, when micropayments
are made, confirmations can be applied automatically without clients'
permission which aims to provide convenience to both merchant and client.  If a
victim's payment code is leaked to the attackers, they can use that code to
authorize multiple micropayments without needing permission.  In order to prevent such
cases, both WeChat Pay~\cite{Wechat-pay} and Alipay~\cite{AliPay} have designed a refreshing mechanism for the
payment code, which is to refresh the QR code every minute. This is sufficient
to stop an attack like sneak shots but unable to stop a real-time attack like our
\tool.  In summary, the payment QR code is highly sensitive on users' devices
and our following case study is about how to obtain this code using an
attacker-crafted power bank via \tool.
